\documentclass[a4paper]{article}
\usepackage[a4paper,margin=0.70in]{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}
\usepackage{xcolor}

\newcommand{\tightsection}[1]{
    % \vspace{0.28em}
  \vspace{-0.9em}
  \section*{#1}
  \vspace{-0.95em}
  {\color{gray}\hrule height 0.5pt}
  \vspace{0.5em}
}


\newcommand{\tightsectionStart}[1]{
  \vspace{-0.70em}
  \section*{#1}
  \vspace{-0.9em}
  \vspace{0.5em}
}

\begin{document}
\fontsize{10.4pt}{10.4pt}\selectfont
\begin{center}
    {\LARGE \textbf{Abey Richard Hurtis}} \\
    St John’s, NL, Canada \textbar abeyhurtis@gmail.com 
    \textbar\href{https://AbeyHurtis.github.io}{https://AbeyHurtis.github.io}
    \textbar \href{https://github.com/AbeyHurtis}{https://github.com/AbeyHurtis} \textbar  \href{https://www.linkedin.com/in/AbeyHurtis}{https://www.linkedin.com/in/AbeyHurtis}
\end{center}


\tightsection{Education}
\textbf{Memorial University of Newfoundland} \\
\textit{Master of Applied Science} (M.A.Sc.) Computer Engineering 
\begin{itemize}
    \item \textbf{Award:} Best Capstone Project Award — Built a high performance 2D convolutional kernel using OpenCL on an Intel DE10-Agilex FPGA, integrated into a U-Net model for brain tumor segmentation.
\end{itemize}


\noindent\textbf{Amal Jyothi College of Engineering} \\
\textit{Bachelor of Technology} (B.Tech.) Computer Science \& Engineering 

% \section*{Experience}
\tightsection{Work Experience}

\textbf{IBM} \hfill \textbf{January 2020} -- \textbf{January 2023} \\
\textit{Systems Engineer (January 2021 -- January 2023)} \\
\textit{Associate Systems Engineer (January 2020 -- December 2020)} 

\vspace{0.5em}
\noindent
\textbf{Client: SELFRIDGES} \\
\textit{Application Developer} \hfill February 2021 -- January 2023  
\begin{itemize}[itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt]
    \item Led the redesign of a legacy database system by migrating from Excel and other systems to MySQL, reducing average query times from \textasciitilde2500ms to \textasciitilde500ms. Enabled parallel API request handling, removing read bottlenecks and improving overall system responsiveness.
    \item Built Python scripts with Pandas to clean and standardize data from legacy sources and customer API documentation, enabling structured storage, migration, and reducing manual fixes downstream.
    \item Developed 10+ Groovy-based backend APIs for order and payment workflows while leading and mentoring a junior engineer.
    \item Coordinated with client QA and managers to validate and deploy all order management APIs using ReadyAPI, ensuring full functional coverage and on-time release.
\end{itemize}

\vspace{0.5em}
\noindent
\textbf{Client: IBM DevSecOps} \\
\textit{DevOps Engineer} \hfill December 2020 -- December 2021  
\begin{itemize}[itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt]
    \item Automated security compliance checks on cloud-provisioned AIX, Linux, and Windows servers using Python, significantly reducing manual auditing workload.
    \item Created a reusable Python framework to standardize OS-specific compliance automation across AIX, Linux, and Windows servers.
    \item Developed a generator script to produce OS-specific compliance checks from high-level system security requirements, eliminating manual script creation.
\end{itemize}

\vspace{0.5em}
\noindent
\textbf{Client: GEICO} \\
\textit{DevOps Engineer} \hfill September 2020 -- November 2020
\begin{itemize}[itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt]
    \item Automated provisioning and Jenkins CI/CD pipelines for staging and production environments.
    \item Built Docker/Kubernetes workflows for web apps, automating environment setup and reducing overhead for developers and DevOps teams.
    \item Deployed containerized services to IBM-managed Kubernetes clusters, enabling consistent, repeatable rollouts across staging and production environments.
\end{itemize}

\tightsection{Projects}
\begin{itemize}[itemsep=1pt,topsep=1pt]
    \item \href{https://AbeyHurtis.github.io}{\textcolor{blue}{\textbf{Portfolio Website}}}(https://AbeyHurtis.github.io): Built a responsive portfolio website using React and TailwindCSS with GSAP powered animations, improving user engagement and showcasing frontend skills to prospective employers; automated deployment to GitHub Pages using GitHub Actions and CI/CD workflows.
    
    \item \href{https://github.com/AbeyHurtis/METAEXPLORE}{\textcolor{blue}{\textbf{MetaExplore}}}(https://github.com/AbeyHurtis/METAEXPLORE): Analyzed metadata from \textasciitilde1 million research papers (2000–2020, S2ORC) using Python, Pytest, Pandas, NumPy and Matplotlib to uncover global publication trends and disparities in scientific research.

    \item \href{https://github.com/AbeyHurtis/FPGA-SoundGen-}{\textcolor{blue}{\textbf{WM8731 Audio Codec}}}(https://github.com/AbeyHurtis/FPGA-SoundGen-): Implemented a hardware based digital audio signal generator on the DE10-Standard FPGA using VHDL to explore I²S protocol behavior and FPGA interfacing; integrated the WM8731 audio codec via I²C and I²S using Quartus.
\end{itemize}


% \section*{Skills}
\tightsection{Skills}
\begin{itemize}[noitemsep,topsep=0pt]
  \item \textbf{Languages}: Python, VHDL, Bash, Shell Scripting, PowerShell Scripting, Groovy
  \item \textbf{Frameworks, Tools and Libraries}:Pandas, NumPy, Matplotlib, React, TailwindCSS, GSAP, Docker, Kubernetes, Jenkins, Git, Linux, ReadyAPI
  \item \textbf{Databases}: MySQL
\end{itemize}
\end{document}